---
title: "odmgm"
output:
  github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  rcomment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


[![DOI](https://zenodo.org/badge/290208715.svg)](https://zenodo.org/badge/latestdoi/290208715)

This research compendium contains `R` code used to conduct the analysis of our work [reference to paper]. The contents are organized as an `R` package and it is therefore possible to install the package, called `odmgm`, as follows. First run the following command

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("mlindsk/odmgm")
```

Secondly, the package suggests the `gRapHD` package, all though no longer maintained on `CRAN`. To install `gRapHD`, first make a git clone, and then call the following command

```{r eval = FALSE}
install.packages("gRapHD/gRapHD_0.2.6.tar.gz", repos = NULL, type = "source")
```

The `gRapHD` package is needed to fit a mixed interaction graph. Currently, the `R` package ecosystem lacks good maintained algorithms for the purpose of model selection in mixed graphical models. We provide the wrapper function `odmgm:::fit_mixed_graph`.

# The Analysis 
The code snippets to reproduce the results in the paper is located in the `analysis` folder.

# Example of Usage
Once the `odmgm` package is intalled

# Cite

If you want to cite the code, please use 

```latex
@software{mlindsk_2020_3999522,
  author       = {mlindsk},
  title        = {mlindsk/odmgm v1.0},
  month        = aug,
  year         = 2020,
  publisher    = {Zenodo},
  version      = {v1.0},
  doi          = {10.5281/zenodo.3999522},
  url          = {https://doi.org/10.5281/zenodo.3999522}
}
```

If you want to cite the method, please use

```latex
TBA
```

# See also
For outlier detection in pure categorical data, see the `R` package (on `CRAN`) [molic](https://github.com/mlindsk/molic). The `molic` package depends on the `R` package (on `CRAN`) [ess](https://github.com/mlindsk/ess) which is designed for efficient model selection in discrete decomposable models.
